---
title: "Introduction to covizr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to covizr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The covizr package provides easy access to Covid-19 data from Our World in Data, as well as functions to generate relevant Covid-19 charts and summaries easily. We aim to make covizr simple and easy to use. Our goal is to enable anyone with basic R programming knowledge to access and visualize Covid-19 data, and make their own informed decisions and conclusions.

We aim to provide simple visualization functions that allow users to answer questions regarding the Covid-19 pandemic as quickly as possible.

This document introduces you to to the basics of using covizr, and shows you how to apply the function.

To use the function, first install the package according to the steps in README, and import the the library with the following code:

```{r setup}
library(covizr)
```

## Data

To explore the usage of covizr, you do not need extra data. Run the following function as the beginning of the code:

```{r getdata, message = FALSE}
df <- get_data()
df
```

By default the function returns the last 7 days of data around the world. There are a few options you can parse into the function for more specific data selection:

* date_from: Start date of the data range with format of 'YYYY-MM-DD'.
* date_to: End date of the data range with format of 'YYYY-MM-DD'.
* location: Charactor vector of target country names.

For example, to retrieve the data between '2021-05-01' to '2021-07-01' of Canada and United Kingdom:

```{r getdata_options, message = FALSE}
loc <- c('Canada', 'United Kingdom')
df <- get_data(date_from = "2021-05-01", date_to = "2021-07-01", location = loc)
df
```
## Visualization functions

### Horizontal bar chart summarising a specified variable and value using `plot_summary`

### Line chart presenting specific countries' Covid information using `plot_spec`

### Line chart presenting Covid total new cases verses another metric using `plot_metric`


