---
title: "Introduction to covizr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to covizr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The covizr package provides easy access to Covid-19 data from Our World in Data, as well as functions to generate relevant Covid-19 charts and summaries easily. We aim to make covizr simple and easy to use. Our goal is to enable anyone with basic R programming knowledge to access and visualize Covid-19 data, and make their own informed decisions and conclusions.

We aim to provide simple visualization functions that allow users to answer questions regarding the Covid-19 pandemic as quickly as possible.

This document introduces you to to the basics of using covizr, and shows you how to apply the function.

To use the function, first install the package according to the steps in README, and import the the library with the following code:

```{r setup}
library(covizr)
```

## Data

To explore the usage of covizr, you do not need extra data. Run the following function as the beginning of the code:

```{r getdata, message = FALSE}
df <- get_data()
df
```

By default the function returns the last 7 days of data around the world. There are a few options you can parse into the function for more specific data selection:

-   date_from: Start date of the data range with format of 'YYYY-MM-DD'.
-   date_to: End date of the data range with format of 'YYYY-MM-DD'.
-   location: Character vector of target country names.

For example, to retrieve the data between '2021-05-01' to '2021-07-01' of Canada and United Kingdom:

```{r getdata_options, message = FALSE}
loc <- c('Canada', 'United Kingdom')
df <- get_data(date_from = "2021-05-01", date_to = "2021-07-01", location = loc)
df
```

## Visualization functions

### Summarising a specified variable and value using `plot_summary`

### Presenting specific countries' Covid information using `plot_spec`

We could also get information from specific countries that interest us. By default, this plot_spec function will plot the last 7 days' new cases trend for Canada. There are a few options you can parse into the function:

-   df: Data frame of the selected covid data from get_data(), note that the date range used in get_data function must match or cover the date range here, in order to get complete result
-   location: Character vector of target country names.
-   val: Quantitative values to be aggregated. Must be numeric variable. Also known as a 'measure'. Available options including new_deaths, reproduction_rate, icu_patients, hosp_patients, etc.
-   date_from: Start date of the data range with format of 'YYYY-MM-DD'.
-   date_to: End date of the data range with format of 'YYYY-MM-DD'.
-   title: The title of the plot.

For example, this plot_spec function below draws the trend of new death cases in Canada and Turkey over the first two weeks of January 2022.

```{r plot_spec, message = FALSE, fig.width=7, fig.height=5}
df <- get_data(date_from="2022-01-01", date_to="2022-01-15")
plot_spec(df, location = c("Canada", "Turkey"), val="new_deaths", date_from="2022-01-01", 
          date_to="2022-01-15", title="Death cases in Canada and Turkey")
```


### Presenting Covid total new cases verses another metric using `plot_metric`
